% vim: set spell spelllang=en tw=100 et sw=4 sts=4 :

\documentclass[a4paper]{article}

\usepackage[inner=1in,outer=1in,top=1in,bottom=1.4in]{geometry}
\usepackage{microtype}                 % the pretty
\usepackage{titlesec}                  % muck around with titles
\usepackage{caption}
\usepackage{complexity}                % \P, \NP etc
\usepackage{varioref}                  % \vref
\usepackage{hyperref}                  % clicky links
\usepackage{cleveref}                  % no need to type Figure etc
\usepackage{tikz}                      % For pretty pictures
\usepackage{amsmath}                   % \text
\usepackage{wrapfig}                   % wrapping figures
\usepackage{pdflscape}
\usepackage[space]{cite}
\usepackage{enumitem}
\usepackage{afterpage}                 % \afterpage
\usepackage{placeins}                  % \FloatBarrier
\usepackage[ruled,vlined]{algorithm2e} % algorithms

\usetikzlibrary{arrows, shadows, calc, positioning, decorations, decorations.pathmorphing,
    decorations.pathreplacing, patterns, tikzmark, fit}

% cref style
\crefname{figure}{Figure}{Figures}
\Crefname{figure}{Figure}{Figures}
\crefname{table}{Table}{Tables}
\Crefname{table}{Table}{Tables}
\crefname{part}{Part}{Parts}
\Crefname{part}{Part}{Parts}
\crefname{section}{Section}{Sections}
\Crefname{section}{Section}{Sections}
\crefname{algocf}{algorithm}{algorithms}
\Crefname{algocf}{Algorithm}{Algorithms}

% captions
\captionsetup[figure]{labelfont=bf}

\setlength{\belowcaptionskip}{6pt}

% titles
\newlength\marginnumberslen
\setlength\marginnumberslen{\dimexpr\oddsidemargin+0.4in+\hoffset\relax}

\titleformat{name=\section}{\normalfont\Large\bfseries}{\llap{\hspace*{-\marginnumberslen}\thesection\hfill}}{0em}{}[{\vspace*{-\baselineskip}\medskip\hspace*{-\marginnumberslen}\textcolor{safelightgrey}{\titlerule}}]

\titleformat{name=\subsection}{\normalfont\large\bfseries}{\llap{\hspace*{-\marginnumberslen}\thesubsection\hfill}}{0em}{}[{\vspace*{-\baselineskip}\medskip\hspace*{-\marginnumberslen}\textcolor{safenearlywhite}{\titlerule}}]


% bibliography
\makeatletter
\let\old@biblabel\@biblabel
\def\@biblabel#1{\llap{\hspace*{-\marginnumberslen}\old@biblabel{#1}\hfill}}%

\let\orig@thebibliography\thebibliography
\renewcommand{\thebibliography}{\labelsep=\z@ \leftmargin=\z@ \orig@thebibliography}
\makeatother

% colours
\definecolor{safelightblue}{rgb}{0.65098, 0.807843, 0.890196}
\definecolor{safedarkblue}{rgb}{0.121569, 0.470588, 0.705882}
\definecolor{safeverylightblue}{rgb}{0.857843, 0.931961, 0.996078}
\definecolor{safeverydarkblue}{rgb}{0.007843, 0.219608, 0.345098}
\definecolor{safelightorange}{rgb}{0.996078, 0.931961, 0.857843}
\definecolor{safelightgreen}{rgb}{0.698039, 0.87451, 0.541176}
\definecolor{safemediumorange}{rgb}{0.74902, 0.505882, 0.490196}
\definecolor{safelightgreen}{rgb}{0.698039, 0.87451, 0.541176}
\definecolor{safedarkgreen}{rgb}{0.2, 0.627451, 0.172549}
\definecolor{safepurple}{rgb}{0.458824, 0.439216, 0.701961}
\definecolor{safedarkorange}{rgb}{0.34902, 0.176471, 0.015686}
\definecolor{safelightgrey}{rgb}{0.7, 0.7, 0.7}
\definecolor{safenearlywhite}{rgb}{0.9, 0.9, 0.9}
\definecolor{safereallynearlywhite}{rgb}{0.93, 0.93, 0.93}

% showframe haxx
\makeatletter
\def\Gm@hrule{\color{safereallynearlywhite}\hrule height 0.2pt depth\z@ width\textwidth}
\def\Gm@hruled{}
\newcommand*{\gmshow@textheight}{\textheight}
\newdimen\gmshow@@textheight
\g@addto@macro\landscape{\gmshow@@textheight=\hsize\renewcommand*{\gmshow@textheight}{\gmshow@@textheight}}
\def\Gm@vrule{\color{safereallynearlywhite}\vrule width 0.2pt height\gmshow@textheight depth\z@}
\makeatother

% drawing styles
\tikzset{vertex/.style={draw, circle, inner sep=0pt, minimum size=0.5cm, font=\small\bfseries}}
\tikzset{notvertex/.style={vertex, color=white, text=black}}
\tikzset{plainvertex/.style={vertex}}
\tikzset{selectedvertex/.style={vertex, fill=safedarkblue}}
\tikzset{delvertex/.style={vertex, dotted, color=safelightgrey}}
\tikzset{vertexc1/.style={vertex, fill=safelightblue}}
\tikzset{vertexc2/.style={vertex, fill=safedarkblue, text=safenearlywhite}}
\tikzset{vertexc3/.style={vertex, fill=safelightorange}}
\tikzset{vertexc4/.style={vertex, fill=safedarkorange, text=safenearlywhite}}
\tikzset{vertexc5/.style={vertex, fill=safedarkgreen}}

\tikzset{edge/.style={color=safelightgrey}}
\tikzset{bedge/.style={ultra thick}}
\tikzset{deledge/.style={dotted, color=safelightgrey}}
\tikzset{edgel1/.style={color=safeverydarkblue}}
\tikzset{edgel2/.style={color=safemediumorange}}
\tikzset{edgel3/.style={ultra thick, color=safedarkblue}}
\tikzset{edgel4/.style={ultra thick, color=safelightorange}}

\tikzset{processarrow/.style={->, very thick, decorate, decoration={snake, post length=0.5mm}}}
\tikzset{brace/.style={decorate, decoration={brace}, thick}}
\tikzset{bracem/.style={decorate, decoration={brace, mirror}, thick}}
\tikzset{label/.style={font=\small}}

% Use these colours to replace the obnoxious defaults used for links in PDFs
\hypersetup{
    colorlinks,
    citecolor=safedarkgreen,
    linkcolor=safedarkblue,
    urlcolor=safepurple}

% \input isn't expandable. yay.
\makeatletter\newcommand*\inputhaxx[1]{\@@input #1}\makeatother

% notation
\newcommand{\vertexset}{V}
\newcommand{\edgeset}{E}
\newcommand{\neighbourhood}{N}
\newcommand{\modularproduct}{\operatorname{\triangledown}}
\newcommand{\graphcomplement}[1]{\shortoverline{#1}}
\newcommand{\Aut}[1]{\operatorname{Aut}{#1}}
\newcommand{\End}[1]{\operatorname{End}{#1}}
\newcommand{\compose}{\circ}
\newcommand{\inverse}{^{-1}}

\newcommand{\Cbest}{C^\star}
\newcommand{\Lbest}{L^\star}
\newcommand{\first}{\mathit{first}}
\newcommand{\bounds}{\mathit{bounds}}
\newcommand{\budget}{\mathit{budget}}
\newcommand{\order}{\mathit{order}}
\newcommand{\colour}{\mathit{colour}}
\newcommand{\clique}{\mathit{clique}}
\newcommand{\uncoloured}{\mathit{uncoloured}}
\newcommand{\remaining}{\mathit{remaining}}
\newcommand{\colourable}{\mathit{colourable}}
\newcommand{\cliqueable}{\mathit{cliqueable}}
\newcommand{\singletons}{\mathit{singletons}}
\newcommand{\expand}{\FuncSty{expand}}
\newcommand{\colourOrder}{\FuncSty{colourOrder}}
\newcommand{\colourOrderDefer}{\FuncSty{colourOrderDefer}}
\newcommand{\cliquePartitionDeferOrder}{\FuncSty{cliquePartitionDeferOrder}}
\newcommand{\vrej}{v_{\mathit{rej}}}
\newcommand{\kwunset}{\KwSty{unset}}

\newcommand{\mclabel}[1]{\label{line:mc:#1}}
\newcommand{\mcline}[1]{line~\ref{line:mc:#1}}
\newcommand{\mclinerange}[2]{lines~\ref{line:mc:#1} to~\ref{line:mc:#2}}
\newcommand{\mcmark}[1]{\tikzmark{mark:mc:#1}}

\makeatletter
\def\blfootnote{\xdef\@thefnmark{}\@footnotetext}
\makeatother

\title{Learning Outcomes}

\author{
    Ciaran McCreesh%
    \\ \href{mailto:c.mccreesh.1@research.gla.ac.uk}{\nolinkurl{c.mccreesh.1@research.gla.ac.uk}}
}

\begin{document}

\makeatletter
\vspace*{1cm}\noindent{\centering\Large\bfseries \@title \par}
\vspace*{1cm}\noindent{\centering \@author \par}
\vspace*{0.5cm}\noindent{\centering \@date \par}
\vspace*{0.5cm}
\makeatother

\begin{itemize}
    \item How to view recursive calls made by a search algorithm as a tree.
    \item Limited discrepancy search:
        \begin{itemize}
            \item What are its assumptions?
            \item When is it likely to be useful?
            \item What are the variations?
        \end{itemize}

    \item Optimisation via parallel decision problems:
        \begin{itemize}
            \item Why is it usually not very successful?
        \end{itemize}

    \item Parallel portfolios.

    \item Parallel consistency and bit parallelism.

    \item Parallel tree searches:
        \begin{itemize}
            \item What does irregular mean? Why is balance a problem?

            \item How does work stealing address balance?

            \item How does Embarrassingly Parallel Search address balance?

            \item How to calculate the potential for speedups?
        \end{itemize}
\end{itemize}

\end{document}

